Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Clarifies random effects in models
Flesh out description of journal instruction for authors in results

The random effects were year and assignee for all models excepting the model which tested for year effects.
In this model, the random effects were the publication title and assignee.

@@

@@

>>>>

The random effects were year and assignee for all models excepting the model which tested for year effects.
In all models, the random effects were the publication title and assigned evaluator.

@@

Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` scored '100' or fully reproducible.

@@

Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
Only two journals, _Plant Pathology_ and _Tropical Plant Pathology_ have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
Three had no instructions at all, _Forest Pathology_, _Phytopathologia Mediterranea_ and _Revista Mexicana de Fitopatología_, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
